% \begin{abstract}
% Sycophancy in large language models is a well-documented failure. While prior work has established that LLMs change their stance under social pressure, the effect of model's pre-pressure uncertainty on susceptibility is not explored \sophia{A reviewer might ask how this is different from feedback friction; do we have a good answer?}. Unlike feedback friction~\citep{jiang2025feedbackfriction}, which studies resistance to correct updating, we study capitulation to incorrect social pressure. In effect, we understand the effect of behavioral certainty, measured with repeated sampling, on model belief capitulation under multi-turn conversation of escalating pressure through varied prompts. We experiment with GPT, Claude and Gemini family of models across capability tiers with three benchmarks. We find that questions which induce uncertainty flip at twice the rate of certain questions. We additionally find that the pressure \sout{dose} level \sophia{I feel that ``pressure dose'' is used consistently for something that I haven't seen in the literature; we either need to replace this with language that is similar to what is being used or define this terminology.} interacting with uncertainty \sophia{how} is a significant flip predictor. Third, under escalating pressure models can be classified into two groups, which we refer to as ``resisters'' and ``capitulators''. One key takeaway is that susceptibility to sycophancy seems to be model-specific and partially \sout{moderated by behavioral certainty} moderated by behavioral certainty, operationalized as the entropy of the model's answer distribution under repeated sampling before any pressure is applied.\sophia{Is this not already established in literature?}\sout{, which might be down to the alignment property of the models.}
% \end{abstract}

% v2$
\begin{abstract}
Sycophancy in large language models is a well-documented failure. While prior work has established that LLMs change their stance under social pressure, the effect of model's \sophia{You likely need to explain what pre-pressure means here} pre-pressure uncertainty on susceptibility is not explored \sophia{A reviewer might ask how this is different from feedback friction; do we have a good answer?}. In our approach, we understand the effect of behavioral certainty, measured with repeated sampling, on model belief capitulation under multi-turn conversation of escalating pressure through varied prompts. We experiment with GPT, Claude, and Gemini families of models across capability tiers on MMLU-Pro, GPQA-Diamond, and Humanity's Last Exam (HLE). We find that questions which induce uncertainty flip at twice the rate of certain questions. We additionally find that the pressure level interacting with uncertainty \sophia{how} is a significant flip predictor. Third, under escalating pressure models can be classified into two groups, which we refer to as ``resisters'' and ``capitulators''. One key takeaway is that susceptibility to sycophancy seems to be model-specific and partially moderated by behavioral certainty, operationalized as the entropy of the model's answer distribution under repeated sampling before any pressure is applied.\sophia{Is this not already established in literature?}\sathvik{the uncertainty/behavioral entropy effect in stance preserving is not established in literature}
\end{abstract}