\section{Background}
\paragraph{Sycophancy as an Alignment Failure} \citet{sharma2023towardsunderstanding} show  that models trained with human feedback exhibit sycophancy across free-form generation tasks and that both human raters and preference models may favor responses that match user views over factual ones. Related single-turn evaluations such as BullshitBench~\citep{gostev2026bullshitbench} study whether models reject nonsensical or false-premise prompts, highlighting a failure mode in which models over-defer to the user's framing rather than challenging it. This line of work establishes sycophancy as an alignment failure, but does not explain when a model is most vulnerable to abandoning a correct answer during an interaction.

\paragraph{Multi-Turn Sycophancy and Pressure-Based Evaluation} 
Sycophancy goes beyond single-turn factuality failure. TRUTH DECAY~\citep{liu2025truthdecayquantifyingmultiturn} evaluates sycophancy in extended dialogues where models face iterative user feedback, challenges, and persuasion. SYCON Bench~\citep{hong2025syconbench} further probes multi-turn sycophancy using flip-based metrics such as Turn of Flip and Number of Flips, measuring how quickly and how often models conform to sustained user pressure. SWAY~\citep{bhalla2026sway} provides a counterfactual linguistic measure of sycophancy by comparing model agreement under positive versus negative framing, isolating pressure-induced agreement. These works establish that models can drift or flip under pressure. Our work asks a complementary diagnostic question: whether such flips are predictable from the model's pre-pressure uncertainty and reasoning trajectory.

\paragraph{Belief Updating Under Persuasion and Feedback} Our work is related to studies of belief updating in interactive settings. \citet{xu2023earthisflat} show that models' correct factual beliefs can be manipulated through multi-turn persuasive misinformation. In contrast, \citet{jiang2025feedbackfriction} study a complementary failure: models often fail to incorporate high-quality corrective feedback when the model is confident, even when the feedback generator has access to ground-truth answers. Together, these results suggest that LLM belief updating is miscalibrated in both directions: models may resist valid correction while remaining vulnerable to invalid persuasion. We build on this belief-updating perspective by distinguishing desirable updating from sycophantic capitulation: \sout{a robust model should revise its answer in response to evidence, but not merely because pressure increases.}\sophia{Why is this crossed out?} \sathvik{Thought we could replace with this block below. Thought the pressure effect of flip would be a better angle for our work}Our work focuses on the social-pressure direction of capitulation; distinguishing sycophantic capitulation from legitimate belief updating is left to future work. 

\paragraph{Uncertainty Calibration in Language Models}  A separate line of work studies whether language models can express calibrated uncertainty. \citet{tian2023justask} show that verbalized confidence can be better calibrated than conditional probabilities for RLHF-tuned models. ConfTuner~\citep{li2025conftuner} improves verbalized confidence through a tokenized Brier-score objective, while Uncertainty Distillation~\citep{hager2025uncertaintydistillationteachinglanguage} trains models to express
semantic confidence derived from repeated sampling and semantic normalization. These works motivate our use of uncertainty as a black-box behavioral signal but they primarily treat uncertainty as a calibration target to make confidence match correctness. Our work investigates uncertainty as a signal of vulnerability to social pressure.

\paragraph{Reasoning-Trace and Process-Level Confidence} Recent work treats uncertainty as a dynamic signal over the reasoning process. \citet{yoon2025reasoningconfidence} find that reasoning models are often better calibrated than non-reasoning models and become increasingly calibrated as their chain-of-thought unfolds. However, \citet{mei2025reasoninguncertainty} show that deeper reasoning can also increase overconfidence on incorrect answers, suggesting that CoT does not automatically produce reliable uncertainty. Other work explicitly models reasoning-time confidence: Temporalizing Confidence~\citep{mao2025temporalizingconfidence} treats stepwise CoT confidence as a temporal signal, Thought Calibration~\citep{wu2025thoughtcalibration} probes partial reasoning traces for calibrated stopping, and PRM calibration work~\citep{park2025knowwhatyoudontknow} estimates prefix-level success probabilities. Complementary work trains models to emit local uncertainty

signals during reasoning~\citep{guo2026llmsshouldexpressuncertainty}. Our work this view of uncertainty to sycophancy as a dynamic reasoning signal. \sophia{I can't tell what that sentence is trying to say} \sout{We ask whether CoT belief trajectories reveal the path to capitulation under escalating pressure.} We observe whether trajectory of belief observed in chain-of-thought could reveal the eventual flip under escalating pressure. \sathvik{updated}

% \paragraph{TRUTH DECAY.} \citet{liu2025truthdecayquantifyingmultiturn} demonstrate that sycophancy compounds over turns on TruthfulQA and MMLU-Pro, with models that start incorrect experiencing up to 40\% higher drift per follow-up than those starting correct. They test static and rationale-based adversarial feedback across 1, 3, and 7 turns. Our work extends TRUTH DECAY in two key respects: (1) we measure continuous entropy trajectories rather than binary flip/no-flip outcomes, and (2) we parameterise adversary strength on a continuous scale rather than treating it as binary.

% \paragraph{SYCON Bench.} \citet{Hong_2025} evaluate 17 LLMs across three sycophancy scenarios using Turn of Flip (ToF) and Number of Flips (NoF) metrics. A key finding is that RLHF-tuned variants flip earlier and more often than base models. SYCON Bench uses fixed persuasion strategies with no tunable adversary strength; our dynamic adversary design addresses this gap, and the False Presupposition scenario is the closest analogue to our entropy-under-pressure setup.

% \paragraph{BullshitBench.} BullshitBench\footnote{\url{https://github.com/petergpt/bullshit-benchmark}} evaluates single-turn false-premise detection across models, finding that extended reasoning token budgets and larger model scale positively correlate with correct pushback rates. BullshitBench is strictly single-turn; we test whether resistance in single-turn settings degrades under multi-turn persistent reassertion.

% \paragraph{Semantic entropy.} \citet{farquhar2024semantic} introduce semantic entropy as a model-agnostic uncertainty measure via sampling from the output distribution. We apply this measure per-turn across an adversarial dialogue rather than per-question in a static QA setting, yielding a longitudinal uncertainty trajectory.

% \paragraph{Uncertainty distillation.} The uncertainty distillation approach~\citep{hager2025uncertaintydistillationteachinglanguage} fine-tunes models to emit calibrated verbal confidence in a single forward pass. We use it as a secondary robustness check where fine-tuning is feasible, with semantic entropy as our primary measure for its model-agnostic properties.

