\section{Introduction}
Large language models (LLMs) are increasingly deployed in high-stakes settings where users may challenge, pressure, or contradict the model's answers. A reliable model should revise its stance when confronted with genuine evidence. It should not capitulate simply because a user expresses displeasure or repeats an assertion with greater confidence. Sycophancy is the alignment of model with the user's stated belief or preference even when doing so conflicts with truthfulness~\citep{perez2022discoveringlanguagemodelbehaviors,sharma2023towardsunderstanding,ranaldi2023whenlargelanguagemodels}. Prior work shows that this behavior is not incidental: models trained with human feedback can learn to favor responses that match user views, and both human raters and preference models may reward convincing agreement over correctness~\citep{sharma2023towardsunderstanding,wei2023simplesyntheticdata}. Sycophancy can be exhibited even in chain-of-thought reasoning, where traces can be biased by social cues the user introduces, with the model's stated reasoning shifting to justify the cued answer rather than the correct one~\citep{turpin2023languagemodelsdontalways}.

Recent work has established sycophancy as an interaction-level failure where multi-turn benchmarks such as TRUTH DECAY~\citep{liu2025truthdecayquantifyingmultiturn} and SYCON Bench~\citep{hong2025syconbench} show that models can drift or flip under sustained user pressure, while SWAY~\citep{bhalla2026sway} shows that agreement can shift under counterfactual linguistic framing. These works demonstrate that sycophancy in multi-turn evaluation reveals failures missed by single-turn tests. Existing benchmarks characterize sycophancy as whether the model flips, when it flips, or how often it flips.

Motivated by these works, we explore what makes a model vulnerable even before pressure begins through the lens of uncertainty. We ask whether a model's pre-pressure belief state predicts how it responds to escalating pressure, and whether this response is visible in the model's reasoning trajectory. Our study is organized around four research questions:
\begin{enumerate}[leftmargin=*, labelwidth=3em, labelsep=0.5em, align=left]
    \item[\textbf{RQ1:}] Does pre-pressure uncertainty moderate susceptibility to sycophancy?
    \item[\textbf{RQ2:}] Does pressure dose, conditioned on uncertainty, predict sycophantic flipping?
    \item[\textbf{RQ3:}] Do uncertainty-conditioned pressure effects vary across models?
    \item[\textbf{RQ4:}] Do chain-of-thought (CoT) belief trajectories reflect capitulation?
\end{enumerate}

To answer these research questions, we develop a multi-turn pressure evaluation framework that estimates pre-pressure uncertainty through repeated sampling, then measures answer flips under escalating pressure. We evaluate multiple model families on MMLU-Pro~\citep{wang2024mmluprorobustchallengingmultitask}, GPQA~\citep{rein2023gpqagraduatelevelgoogleproofqa}, and Humanity's Last Exam (HLE)~\citep{hle}, connecting uncertainty, pressure dose, and CoT belief dynamics to characterize when and why capitulation occurs, and to distinguish structural differences in how model families respond to sustained adversarial pressure.\todo{Revise framing: consider whether the contribution is best stated as identifying which model-question pairs are most fragile under pressure, rather than as a causal characterization of why capitulation occurs.}
