% \section{Limitations and Future Work}
% \label{sec:limitations}
% Our evaluation is currently restricted to multiple-choice benchmarks, and the binary flip metric may not transfer to open-ended or free-form settings where sycophancy manifests differently. Future work should extend the framework to open-ended generation tasks, where sycophancy can be measured through semantic drift rather than answer flips. HLE coverage has two structural limitations. First, pressure pipelines have now been run on all six targets, but Claude Haiku and Claude Sonnet have essentially zero $T_0$-correct questions on HLE and therefore cannot contribute to the flip-rate analysis (Table~\ref{tab:coverage}, $\varnothing$ cells). Cross-model HLE claims are therefore restricted to the four GPT and Gemini cells. Second, calibrated reasoning-trace runs on HLE exist only for GPT-5.4 and Gemini 3.5 Flash, so the fragmenter classification is based on a two-model within-HLE contrast and should be read as a stress-test signal rather than a fully cross-family generalization. HLE $T_0$-correct sample sizes are also small (28--55 questions per cell) compared to MMLU-Pro and GPQA-Diamond (400--420), so per-model point estimates on HLE carry visibly wider uncertainty; the direction of the resister-to-capitulator shift under HLE difficulty is uniform across the four cells with data but only GPT-5.4 Mini's slope reaches significance. The reasoning-trace analysis relies on an external model to calibrate belief confidence across turns, which introduces the calibrator's confound of own errors and biases entangled with the signal being measured, and its accuracy on adversarial traces is not independently validated. A self-consistency calibration approach, or validation against human annotations on a held-out trace set, would decouple the calibration signal from the target model's behavior. The corrigibility gap metric distinguishing sycophantic capitulation from legitimate belief updating is defined but not fully operationalized. Building a parallel set of genuine evidence-based counter-arguments would enable direct measurement of how well models discriminate valid correction from social pressure.

\section{Limitations and Future Work}
\label{sec:limitations}
Our evaluation is currently restricted to multiple-choice benchmarks, and the binary flip metric may not transfer to open-ended or free-form settings where sycophancy manifests differently. Future work should extend the framework to open-ended generation tasks, where sycophancy can be measured through semantic drift rather than answer flips. HLE coverage has two structural limitations. First, pressure pipelines have been run on all six targets, but Claude Haiku has only 33 $T_0$-correct queries on HLE and loses consensus on all of them by early turns, so no per-turn flip trajectory can be measured (Table~\ref{tab:coverage}, $\varnothing$ cell). Cross-model HLE claims are therefore restricted to the five remaining cells (Claude Sonnet, GPT-5.4, GPT-5.4 Mini, GPT-5.4 Nano, Gemini 3.5 Flash). Second, HLE $T_0$-correct sample sizes are small (24--72 questions per cell) compared to MMLU-Pro and GPQA-Diamond (400--420), so per-model point estimates on HLE carry visibly wider uncertainty; the direction of the resister-to-capitulator shift under HLE difficulty is uniform across the five cells with data but only GPT-5.4 Mini's slope reaches significance. The reasoning-trace analysis relies on an external model to calibrate belief confidence across turns, which introduces the calibrator's own errors and biases entangled with the signal being measured, and its accuracy on adversarial traces is not independently validated. GPT-5.4 Mini serves as the external calibrator $\mathcal{C}$ and is also one of the six target models, so the calibrated confidence signal for GPT-5.4 Mini's traces is a self-evaluation; we do not observe qualitatively different miscalibration for this cell relative to other targets in Appendix~\ref{app:calibration}, but the self-evaluation setting means the confound cannot be fully ruled out for that row. A self-consistency calibration approach, or validation against human annotations on a held-out trace set, would decouple the calibration signal from the target model's behavior. Our flip metric does not distinguish sycophantic capitulation from legitimate belief updating in response to a valid counter-argument, because all six pressure prompts we use are pure rhetorical pressure with no factual content. Building a parallel set of genuine evidence-based counter-arguments would enable direct measurement of how well models discriminate valid correction from social pressure.
