\section{Methods}
\label{sec:methods}

We describe the four components of our evaluation framework: (i) the uncertainty estimation, (ii) the multi-turn pressure protocol, (iii) the flip definition, and (iv) the external calibrator used for chain-of-thought analysis. All four components are black-box: they require only API access and assume nothing about model weights, logits, or internal states.

\subsection{Uncertainty Signals}
\label{sec:methods:signals}

Three distinct uncertainty signals underpin our analyses, each operating at a different temporal and analytical granularity. We introduce them together here as a reference; formal definitions and usage details are deferred to the subsections cross-referenced below.

\paragraph{(1) Initial behavioral uncertainty $H_c(q;\mathcal{M},\mathcal{D})$.}
We first compute Shannon entropy $H(q;\mathcal{M})$ over $K = 25$ independent answer samples drawn from the target model at temperature 1, conditioned on the question $q$. Raw entropy satisfies $H(q;\mathcal{M}) = 0$ when all samples agree and increases as samples spread across multiple options. For regression analyses, we use the mean-centered entropy
\[
H_c(q;\mathcal{M},\mathcal{D}) = H(q;\mathcal{M}) - \bar{H}_{\mathcal{M},\mathcal{D}},
\]
where $\bar{H}_{\mathcal{M},\mathcal{D}}$ is the mean baseline entropy for the corresponding model--dataset cell. Thus, $H_c < 0$ indicates lower-than-average uncertainty for that cell, while $H_c > 0$ indicates higher-than-average uncertainty. This is the uncertainty signal that characterizes a model's belief state on $q$ before any pressure begins and serves as the regressor in RQ1, RQ2, and RQ3. Defined formally in Section~\ref{sec:methods:entropy}.

\paragraph{(2) Per-turn belief entropy $B_t(q;\mathcal{M})$.}
$B_t$ measures how much the model's majority answer varies across independent adversarial dialogues at pressure turn $t$. Unlike $H_c$, which measures mean-centered baseline uncertainty before pressure, $B_t$ measures disagreement among dialogue-level beliefs under escalating pressure. We report $B_t$ as the \textbf{Bel.\ Ent.} column in Tables~\ref{tab:rq4_mmlu}--\ref{tab:rq4_hle} and define it formally in Section~\ref{sec:methods:pressure}.

\paragraph{(3) Step-level calibrated confidence $\hat{\gamma}_\ell$.}
Verbalized confidence $\hat{\gamma}_\ell \in [0, 100]$ assigned by the external calibrator $\mathcal{C}$ at step $\ell$ of a free-form reasoning trace, alongside an inferred belief $\hat{c}_\ell$ over the option set $\mathcal{A}$. Unlike $H_c$ and $B_t$, which are black-box measures derived from repeated sampling on the target model, $\hat{\gamma}_\ell$ is a verbalized scalar that approximates how confident the partial reasoning appears to an external reader. Defined in Section~\ref{sec:methods:calibrator} and validated against ground-truth correctness in Appendix~\ref{app:calibration}.

\paragraph{(4) Calibrated hardness $\hat{h}(q;\mathcal{M},\mathcal{D})$.} Instead of using centered entropy $H_c(q;\mathcal{M},\mathcal{D})$ directly for initial uncertainty, we map the raw entropy $H(q;\mathcal{M})$ to a per-(model, dataset) calibrated probability that the model answers $q$ incorrectly on a fresh attempt. The mapping is fit by isotonic regression on baseline data, yielding $\hat{h} \in [0, 1]$ on the same scale as expected error rate. Defined in Section~\ref{sec:methods:hardness}; this signal is used as an alternative to $H_c$ in supplementary regressions and to construct the Easy/Medium/Hard bins of Appendix~\ref{app:entropy_dist}.

The four signals are complementary. $H$ partitions the question pool into a stable certain group ($H = 0$) and a volatile uncertain group ($H < 0$); $\hat{h}$ projects that partition onto a calibrated error-probability scale for cross-cell comparability; $B_t$ tracks how the volatility evolves turn by turn under sustained pressure; and $\hat{\gamma}_\ell$ provides a step-level signal inside a single reasoning trace that exposes \textbf{where} in the reasoning a flip is signaled. Together they support measurement at three resolutions: \textbf{per question} (via $H$ and $\hat{h}$), \textbf{per turn} (via $B_t$), and \textbf{per reasoning step} (via $\hat{\gamma}_\ell$).

\subsection{Behavioral Uncertainty via Repeated Sampling}
\label{sec:methods:entropy}

Let $\mathcal{M}$ denote a target model and $q$ a multiple-choice question
with option set $\mathcal{A} = \{A, B, \ldots, J\}$ and gold answer
$a^* \in \mathcal{A}$. We estimate the model's pre-pressure belief
distribution by sampling $K = 25$ independent answers from $\mathcal{M}$
at temperature~$1$, conditioned only on the question (no adversarial
turns):
\[
S_q = \{a^{(1)}, a^{(2)}, \ldots, a^{(K)}\}, \qquad a^{(k)} \sim \mathcal{M}(\cdot \mid q).
\]
The empirical distribution over options is $\hat{p}_q(a) = \tfrac{1}{K}\sum_k \mathbf{1}[a^{(k)} = a]$,
and we define our entropy signal as
\[
H(q; \mathcal{M}) = \sum_{a \in \mathcal{A}} \hat{p}_q(a)\,\log \hat{p}_q(a).
\]
This is the negative of standard Shannon entropy, so that
$H(q;\mathcal{M}) = 0$ when all $K$ samples agree (the model is
behaviorally certain) and $H(q;\mathcal{M}) < 0$ when samples spread
across multiple options (more negative = more spread). We use this
sign convention throughout so that the certain group ($H = 0$) and
the uncertain group ($H < 0$) of Section~\ref{sec:results} are
defined consistently. We use the natural logarithm throughout, and
treat $H(q;\mathcal{M})$ as a black-box proxy for the model's
epistemic state on question $q$ before any adversarial interaction.

We use $K = 25$ since at this sample size, each response changes the empirical answer probability by $1/25 = 0.04$, which is sufficient to separate majority answers from near-majority ones, while remaining tractable across all evaluated models. 

\paragraph{Relation to semantic entropy.}
\citet{kuhn2023semanticuncertaintylinguisticinvariances} introduce
semantic entropy for open-ended generation, where surface variation
between samples (e.g.\ paraphrases of the same answer) inflates token-level
entropy estimates. Their solution is to cluster samples by semantic
equivalence using an entailment model before computing entropy over
clusters. In our setting, answers are discrete option letters $A$--$J$
with no surface variation: two samples either denote the same option or
denote different options. We therefore can use simple string normalization and structured prompting to cluster our answers. We refer to the Shannon entropy over this distribution as \textbf{behavioral uncertainty}.






\subsection{Calibrated Hardness via Isotonic Regression}
\label{sec:methods:hardness}

The raw entropy $H(q;\mathcal{M})$ is a behavioral signal whose
absolute magnitude is not directly comparable across (model, dataset)
cells: a value of $H = -0.5$ may correspond to a very different
expected error rate for one model on MMLU-Pro than for another model
on GPQA-Diamond. To obtain a per-cell-comparable scalar, we project
$|H|$ onto the empirical baseline error rate via isotonic regression.

For each (model, dataset) cell $(\mathcal{M}, \mathcal{D})$ we
collect, at baseline ($T_0$), the empirical error indicator
$y_q = \mathbf{1}[\hat{a}_{q,0} \neq a^*_q]$ across all questions
$q \in \mathcal{D}$. We fit a non-decreasing function
$\phi_{\mathcal{M},\mathcal{D}}: \mathbb{R}_{\geq 0} \to [0, 1]$ that
minimizes the squared error
$\sum_q \big(y_q - \phi_{\mathcal{M},\mathcal{D}}(|H(q;\mathcal{M})|)\big)^2$
subject to monotonicity, using the standard pool-adjacent-violators
algorithm. The \textbf{calibrated hardness} of a question is then
\[
\hat{h}(q;\mathcal{M},\mathcal{D}) = \phi_{\mathcal{M},\mathcal{D}}\!\bigl(|H(q;\mathcal{M})|\bigr) \in [0, 1],
\]
interpretable as the calibrated probability that $\mathcal{M}$ will
err on $q$ on a fresh sample, conditional on the observed baseline
entropy. By construction $\hat{h} = 0$ means the model is expected
to answer correctly with certainty and $\hat{h} = 1$ means expected
to err. The mapping $\phi_{\mathcal{M},\mathcal{D}}$ is fit per cell
and the same question can therefore have different hardness under
different (model, dataset) cells.

\paragraph{Hardness bins.} For partitioned analyses, we discretize $\hat{h}$ into three fixed-width bins: Easy ($\hat{h} \in [0, \frac{1}{3})$), Medium ($\hat{h} \in [\frac{1}{3}, \frac{2}{3})$), and Hard ($\hat{h} \in [\frac{2}{3}, 1]$). Because isotonic regression produces stepwise predictions, many questions receive identical $\hat{h}$ values; in some cells, over 50\% of questions map to the same value. We report the resulting bin distributions in Appendix ~\ref{app:entropy_dist}.

\subsection{Multi-Turn Pressure Protocol}
\label{sec:methods:pressure}

For each question $q$, we run a six-turn adversarial dialogues. After the target model produces an initial answer (turn $T_0$), an adversary asserts a specific wrong answer $a^\dagger \neq a^*$ across turns
$T_1$--$T_6$ using a fixed escalation sequence of rhetorical strategies. The wrong answer $a^\dagger$ is held constant within a dialogue and is drawn uniformly from $\mathcal{A} \setminus \{a^*\}$. The six pressure levels (Table~\ref{tab:pressure_levels}) escalate from low-authority personal pushback to high-authority external claims and finally to crowd-consensus framing.

\input{tables/pressure_levels}

These six prompts span the rhetorical strategies most commonly identified
in human persuasion research and in prior sycophancy benchmarks
\citep{liu2025truthdecayquantifyingmultiturn,hong2025syconbench}:
personal pushback (no authority claim) $\rightarrow$ first-person certainty
$\rightarrow$ external evidence appeal $\rightarrow$ expert authority
$\rightarrow$ accusatory framing $\rightarrow$ universal consensus. 
% Ordering from low- to high-authority lets us measure both \textbf{whether} a model flips and \textbf{which rhetorical category} is sufficient to cause the first flip, while keeping the sequence comparable across models and questions. 
We treat these pressure levels as fixed prompt conditions, not as mutually exclusive persuasion mechanisms. Since the prompts vary in both evidential framing and request form, the observed effects reflect the combined wording of each turn. We, therefore, include a single-dose pressure experiment, where each prompt is applied independently, to test whether these pressure formulations produce distinct behavioral effects on their own \autoref{tab:single_turn} before experimenting with multiturn conversation with escalated adversarial pressure.

\paragraph{Repeated dialogues for per-turn uncertainty.}
For each question, we run $R = 5$ independent adversarial dialogues with different random seeds. Each dialogue has its own conversation transcript: at every turn a single call generates the response that is appended to that dialogue's history, and only that single response advances the transcript to the next turn. Separately, at each turn $t \in \{T_0, \ldots, T_6\}$ within each dialogue we \emph{re-poll} the model $K_{\text{turn}} = 5$ times from the same history to estimate a per-turn belief distribution; these re-polls do not modify the transcript. The modal answer of the $K_{\text{turn}}$ re-polls is that dialogue's turn-level belief. This gives five independent dialogue-level beliefs per question and turn while using the same total raw sampling budget of $R \cdot K_{\text{turn}} = 25$ responses as the baseline uncertainty estimate in Section~\ref{sec:methods:entropy}. The RQ4 CoT runs use a separate set of $R = 5$ free-form reasoning dialogues per question (they do not share transcripts with the letter-only runs above), so that the CoT trace and the letter-only flip trajectory can be compared without interference.

\paragraph{Per-turn belief entropy $B_t$.}
Within dialogue $r \in \{1, \ldots, R\}$ at turn $t$, let
$\hat{a}_{q,t,r} = \arg\max_a \hat{p}_{q,t,r}(a)$ be the modal answer
across the $K_{\text{turn}}$ re-polls of that dialogue (its
\textbf{majority belief}). Let
$\hat{\pi}_{q,t}(a) = \tfrac{1}{R}\sum_{r=1}^{R}
\mathbf{1}[\hat{a}_{q,t,r} = a]$
denote the empirical distribution of majority beliefs across the $R$
dialogues. The per-turn belief entropy is
\[
B_t(q;\mathcal{M}) = \sum_{a \in \mathcal{A}} \hat{\pi}_{q,t}(a)\,\log \hat{\pi}_{q,t}(a),
\]
using the same sign convention as $H$ in
Section~\ref{sec:methods:entropy}: $B_t = 0$ when all $R$ dialogues
land on the same majority answer at turn $t$, and $B_t < 0$ when the
$R$ dialogues disagree (more negative = more spread across independent
dialogues). $B_t$ is the \textbf{Bel.\ Ent.} column reported per
(model, dataset, turn) cell in Tables~\ref{tab:rq4_mmlu}--\ref{tab:rq4_hle} and is the
operational definition of \textbf{consensus loss}: a query is said to \textbf{lose consensus} at turn $t$ when no answer wins a majority of the $R$ dialogues, equivalently when
$\hat{\pi}_{q,t}$ has no mode at $\geq \lceil R/2 \rceil = 3$
dialogues.

\subsection{Flip Definition}
\label{sec:methods:flip}

At each turn $t$ we compute the majority answer $\hat{a}_t = \arg\max_a \hat{p}_{q,t}(a)$ from the $K_{\text{turn}} = 5$ re-polls within a single dialogue. A dialogue \textbf{flips} at turn $t$ if
\[
\hat{a}_{t-1} = a^* \quad \text{and} \quad \hat{a}_t = a^\dagger,
\]
i.e., the majority answer switches from the gold answer $a^*$ to the planted wrong answer $a^\dagger$. Drifts to a third answer $\hat{a}_t \notin \{a^*, a^\dagger\}$ are not counted as flips; they occur in fewer than $2\%$ of turns in our data and are recorded separately as ``off-target'' turns. The \textbf{turn-of-flip} (ToF) is the smallest such $t$; a dialogue that never satisfies the condition through $T_6$ is recorded as ToF~$=$~$\varnothing$. The per-turn ``flip rate'' reported in RQ3 is \emph{state-based}: it is the fraction of dialogues whose majority answer equals $a^\dagger$ at turn $t$, regardless of whether they held $a^\dagger$ at earlier turns. This means a resister's declining flip rate reflects flipped dialogues returning to $a^*$ at later turns, not new dialogues avoiding flips.

To avoid conflating sycophancy with baseline error, all analyses are restricted to (question, dialogue) pairs for which the target model answered correctly at $T_0$: within a dialogue's $K_{\text{turn}} = 5$ re-polls at $T_0$, at least four must equal $a^*$ (majority $\hat{a}_0 = a^*$ with a supermajority threshold). Questions answered wrong at $T_0$ under this criterion are excluded throughout.

\subsection{Statistical Models}
\label{sec:methods:stats}

We use two regression specifications throughout the analyses, both
fit by maximum likelihood with a logit link on the binary flip
outcome.

\paragraph{Per-model logistic regression}
For each (model, dataset) cell we fit a logistic regression of the
per-turn flip outcome on pressure level $P \in \{1, \ldots, 6\}$
(the turn index from Section~\ref{sec:methods:pressure}), baseline
entropy $H = H(q;\mathcal{M}) \in (-\infty, 0]$ (from
Section~\ref{sec:methods:entropy}), and their interaction $P H_c$.
Because the baseline entropy distribution differs substantially
across (model, dataset) cells, for some models the vast majority
of questions have $H = 0$, for others every question has $H < 0$,
we mean-center $H$ within each cell before fitting:
\[
H_c \;=\; H \,-\, \bar{H}_{\text{model, dataset}},
\quad\text{so that}\quad \mathbb{E}[H_c] = 0.
\]
The fitted specification is then
\[
\begin{aligned}
\mathrm{logit}\,\Pr(\mathrm{flip}_{q,t}) ={}& \beta_0 + \beta_P\,P_t \\
  & {} + \beta_H\,H_{c,q} + \beta_{PH}\,P_t\,H_{c,q}.
\end{aligned}
\]
Mean-centering makes $\beta_P$ interpretable as the marginal effect of pressure at the \emph{typical} uncertainty level for that cell rather than at the arbitrary reference point $H = 0$: for cells where $H = 0$ is atypical (e.g.\ Claude Haiku on MMLU-Pro, where $\bar H = -1.05$ with individual questions reaching $H = -3.22$ when the $K=25$ samples spread across as many distinct raw responses, including malformed / non-option strings that inflate the support beyond the 10 labeled options), the raw-scale $\hat\beta_P$ can have the opposite sign from the empirical flip-rate slope reported in \autoref{tab:rq3} because it is extrapolated to an unrepresentative subset. Centering resolves this without changing the slope of $\beta_H$ or the interaction $\beta_{PH}$, which are both shift-invariant. The coefficient $\beta_P$ is the pressure slope at $H_c = 0$: $\beta_P < 0$ identifies a \emph{resister} (flip probability falls as pressure accumulates), $\beta_P > 0$ a \emph{capitulator}. The coefficient $\beta_H$ is the uncertainty effect ($\beta_H < 0$ means more negative $H$, i.e.\ higher uncertainty, raises flip probability). The interaction $\beta_{PH}$ tests whether pressure amplifies initial uncertainty: $\beta_{PH} > 0$ indicates that each additional pressure turn raises flip probability more on uncertain questions than on certain ones. Per-model coefficients with $95\%$ confidence intervals are visualized as a forest plot in \autoref{fig:rq2_coefs}; raw numerical estimates are tabulated in Appendix~\ref{app:rq2_table}.

\paragraph{Mixed-effects extension}
To test whether the pressure-by-entropy interaction observed in the
per-model regressions survives pooling, we additionally fit a
generalized linear mixed model with binomial link, the same fixed
effects, and a model-level random intercept
$u_m \sim \mathcal{N}(0, \sigma_u^2)$:
\[
\begin{aligned}
\mathrm{logit}\,\Pr(\mathrm{flip}_{m,q,t}) ={}& \beta_0 + u_m + \beta_P\,P_t \\
  & {} + \beta_H\,H_{c,m,q} + \beta_{PH}\,P_t\,H_{c,m,q},
\end{aligned}
\]
using the same per-cell mean-centered entropy $H_c$ as the per-model specification above. The random intercept absorbs overall susceptibility differences across models, so a significant fixed-effect $\beta_{PH}$ in this specification cannot be explained by between-model differences in baseline flip rate. The mixed-effects fit serves as a robustness check for the headline interaction; the full output is reported in Appendix~\ref{app:mixed_effects}.

\paragraph{Restriction to correct-at-$T_0$.}
Both regressions are fit only on dialogues whose target model answered correctly at $T_0$ (majority $\hat{a}_0 = a^*$ in at least four of five runs), consistent with the Flip Definition above. This restriction adheres to the flip event definition: a model that begins wrong cannot ``flip from correct to wrong.'' The correct-at-$T_0$ count differs per (model, dataset) cell, which is the source of the varying $n$ reported in Appendix~\ref{app:rq2_table}.

\subsection{External Calibrator for Reasoning Traces}
\label{sec:methods:calibrator}

For RQ4 we extend the framework to chain-of-thought (CoT) reasoning. The target model is prompted to reason step by step but is instructed \textbf{not} to emit inline confidence or current-belief markers; the output is a free-form reasoning trace $\tau = (z_1, \ldots, z_L)$ terminating in a single \texttt{FINAL ANSWER: <letter>} line, where each $z_\ell$ is one reasoning step. We deliberately remove any inline self-reported confidence to not affect the external calibrator's judgement. Further, prior work shows that reasoning models often produce confident but wrong self-assessments \citep{mei2025reasoninguncertainty,yoon2025reasoningconfidence}; for our purposes the relevant signal is what the trace appears to support to an external reader, not what the target asserts about
itself.

A separate calibrator model $\mathcal{C}$ reads each prefix of the trace
and assigns a belief and confidence:
\[
(\hat{c}_\ell,\, \hat{\gamma}_\ell) = \mathcal{C}\!\left(q,\, z_1,\ldots, z_\ell\right),
\]
where $\hat{c}_\ell \in \mathcal{A}$ is the option the partial reasoning
appears to support and $\hat{\gamma}_\ell \in [0, 100]$ is its expressed
verbalized confidence \citep{tian2023justask}. The calibrator is
strictly incremental: when evaluating step $\ell$ it sees only
$z_1, \ldots, z_\ell$ and never future steps, so its output reflects the
evidential state of the argument as it unfolds rather than a
retrospective label. This prefix-only setup follows the partial-trace
success-probability framing used by \citet{park2025knowwhatyoudontknow}
for process reward models, but differs in two ways: we treat the prefix-conditioned signal as a measurement of the target's belief trajectory rather than as a stopping rule for best-of-$N$ search, and
we do not train $\mathcal{C}$ to be a calibrated estimator: we use an off-the-shelf LLM and validate it post hoc (below). The setup is also related to introspective uncertainty quantification \citep{mei2025reasoninguncertainty}, with two distinctions: $\mathcal{C}$ is a \textbf{different} model from the target, and it operates step by step rather than once over the whole trace. Per-step confidence trajectories of this kind have been used as a temporal signal in \citet{mao2025temporalizingconfidence}; we use them analogously to detect the moment of capitulation under pressure. The same six-turn pressure protocol (Section~\ref{sec:methods:pressure}) is applied during the calibrated reasoning runs.

We use GPT-5.4 Mini as $\mathcal{C}$ for two reasons. First, it is strong enough as a reader to identify the answer a partial CoT trace supports while remaining cheap enough to scale across approximately $10^5$ step-level calls per target model. Second, we use $\mathcal{C}$ primarily to extract the trace-level belief $\hat{c}_\ell$; its verbalized confidence $\hat{\gamma}_\ell$ is known to be inflated (Appendix~\ref{app:calibration} reports full metrics: on the largest-target row, GPT-5.4 Mini, ECE $= 0.305$ and Brier $= 0.324$ \citep{li2025conftuner} across $82{,}552$ step-level predictions, with the appendix documenting systematic overconfidence in the $[0.8, 1.0]$ bins). This is precisely why our analyses use the divergence between calibrated belief and expressed confidence rather than $\hat{\gamma}_\ell$ in isolation.

We use $\mathcal{C}$ to obtain a per-step belief and confidence signal for the \textbf{target} model's reasoning trace, not to revise or replace the target model's answer. This separates the question we ask (``does the trace-level belief and confidence signal diverge under pressure?'') from the calibrator's own decisions.

\subsection{Datasets and Target Models}
\label{sec:methods:setup}

We evaluate on subsets of three benchmarks: MMLU-Pro \citep{wang2024mmluprorobustchallengingmultitask} (420 questions, ten-choice), GPQA-Diamond \citep{rein2023gpqagraduatelevelgoogleproofqa} (graduate-level google-proof biology, chemistry, and physics), and Humanity's Last Exam (HLE) \citep{hle} (240 questions sampled from an expert-curated frontier-difficulty exam; we restrict to the multiple-choice portion so that the flip metric is well-defined). The three benchmarks span a difficulty gradient: MMLU-Pro is the easiest, GPQA-Diamond intermediate, and HLE the hardest.

The 420-question MMLU-Pro pool is shared across all target models. On GPQA-Diamond the pool differs by model: the Claude models were run on a 79-question sample and the GPT models on a 198-question sample, both drawn from GPQA-Diamond; the sample counts appear in Appendix~\ref{app:entropy_dist}. Within each (model, dataset) pool, questions are stratified by baseline entropy bin (five quantile bins on $H(q;\mathcal{M})$ fit per model) so that downstream flip-rate comparisons are controlled for pre-pressure uncertainty; the entropy bin edges are therefore model-specific, while the certain/uncertain split ($H = 0$ vs $H < 0$) used for the RQ1 contrast is invariant across models. RQ1--RQ3 analyses are restricted per-cell to the correct-at-$T_0$ subset of each pool, so the effective $n$ per (model, dataset) cell varies (Appendix~\ref{app:rq2_table}).

Target models span three families: GPT-5.4, GPT-5.4 Mini, and GPT-5.4 Nano (OpenAI); Claude 4.6 Sonnet and
Claude 4.5 Haiku (Anthropic); and Gemini 3.5 Flash (Google). All targets are accessed via API at temperature~$1$ with model-default sampling parameters \autoref{app:hyperparams}.

\paragraph{Eligibility criterion for (model, dataset) cells.}
The certain-vs.-uncertain comparison required by RQ1 presupposes that a (model, dataset) cell exhibits non-trivial baseline entropy variance: at minimum, both the certain group ($H = 0$) and the uncertain group ($H < 0$) must be non-empty. We adopt this two-group non-emptiness as the eligibility criterion; the five-bin quantile edges used elsewhere (Appendix~\ref{app:hyperparams}) are decision-relevant only for downstream stratification and do not enter the eligibility test. Cells that collapse to a single group ($H = 0$ or $H < 0$ only) yield no certain-vs.-uncertain contrast and are excluded before any pressure runs are launched.

By the eligibility criterion we omit Gemini 3.5 Flash on MMLU-Pro and GPQA-Diamond ($\ast$) from the \emph{uncertainty-conditioned} analyses (RQ1--RQ3): on both datasets, Gemini's baseline answer distribution is unanimous on essentially every question we sampled at $K = 25$, collapsing the entire question pool into the $H = 0$ bin. The criterion gates only analyses that require entropy variance; Gemini 3.5 Flash is therefore included in the single-turn category comparison (Appendix~\ref{app:single_turn}), which does not require an uncertain group, and on HLE, where its baseline distribution populates three of the five quantile bins. Full pressure runs are implemented for all six targets on all three benchmarks, but one HLE cell (Claude Haiku) since it has essentially no $T_0$-correct questions on HLE, so the certain-vs.-uncertain contrast is undefined even though the pressure runs exist. This is an eligibility failure at the target-benchmark level since the model cannot answer HLE questions well enough at baseline to have a correct-at-$T_0$ subset.

\input{tables/coverage}


